Manuscript for a Data Analysis Project: Diabetes Diagnosis

### 2024-08-08 products/manuscript/Manuscript.qmd
Final Project Submission
Fixed bibtex and added a few more things to the manuscript. Added the figures as images since knit was being strange about loading images.

This dataset comes from UC Irvine Machine Learning Repository. This data has been gathered and processed from the CDCs website in 2014. This dataset includes over 250,000 instances (observations) and 21 features, ranging from personal information (income/education) to health history (drinking/smoking/physical health). Bellow are the features and there respective descriptions

@@

|---------------------|---------------------------------------------------|

@@

```{r}
knitr::include_graphics(here("results","figures","variable-distributions.png"))
```

@@

```{r}
knitr::include_graphics(here("results","figures","correlation_matrix.png"))
```

@@

```{r}
knitr::include_graphics(here("results","figures","importance_table.png"))
```

@@

```{r}
knitr::include_graphics(here("results","figures","variable_importance.png"))
```

@@

```{r}
knitr::include_graphics(here("results","figures","model_accuracy_comparison.png"))
```

@@

@@

For some reason my bib file was being weird, will try to fix.

>>>>

This dataset comes from UC Irvine Machine Learning Repository. This data has been gathered and processed from the CDCs website in 2014. This dataset includes over 250,000 instances (observations) and 21 features, ranging from personal information (income/education) to health history (drinking/smoking/physical health)[@UCI]. Bellow are the features and there respective descriptions

@@

|----------------------|--------------------------------------------------|

@@

![](images/variable-distributions.png){fig-align="center"}

```{r}
#knitr::include_graphics(here("results","figures","variable-distributions.png"))
```

@@

![](images/correlation_matrix.png){fig-align="center"}

```{r}
#knitr::include_graphics(here("results","figures","correlation_matrix.png"))
```

@@

![](images/importance_table.png){fig-align="center" width="300"}

```{r}
#knitr::include_graphics(here("results","figures","importance_table.png"))
```

@@

![](images/variable_importance.png){fig-align="center"}

```{r}
#knitr::include_graphics(here("results","figures","variable_importance.png"))
```

@@

![](images/model_accuracy_comparison.png){fig-align="center"}

```{r}
#knitr::include_graphics(here("results","figures","model_accuracy_comparison.png"))
```

@@

**Strengths:**

-   **Large Dataset**: The study utilized a large dataset with over 250,000 observations, providing a large sample size for reliable statistical analysis and model training.

-   **Comprehensive Features**: The dataset had 21 diverse features ranging from personal information to health history, allowing for a thorough analysis of various health indicators.

-   **Multiple Models**: The use of three different models (logistic regression, random forest, and KNN) provided a comprehensive approach to identifying key predictors and comparing model performances.

**Limitations:**

@@
